OA Share

### 2021-05-19 analysis/006_license.Rmd

```{r}
library(cowplot)
p_1 <- year_per_oa_type_and_license %>%
  mutate(type_plot = case_when(
    type == "full_oa" ~ "Full OA",
    type == "hybrid_immediate_articles" ~ "Hybrid OA",
    type == "hybrid_delayed_articles" ~ "Delayed OA"
  )) %>% 
  mutate(type_plot = factor(type_plot, levels = c("Hybrid OA", "Full OA", "Delayed OA"))) %>%
  ggplot(aes(gsub("20", "'", as.character(issued_year)), prop, fill = license_code, group = license_code)) +
  geom_area(stat = "identity",
            color = "white",
            alpha = 0.8,
            position = position_stack(reverse = T)) +
  facet_grid(~type_plot) +
  scale_y_continuous(
    expand = expansion(mult = c(0, 0.0005)),
    labels = scales::percent_format(accuracy = 1L),
    breaks = c(0, 0.02, 0.04, 0.06, 0.08)
  ) +
  scale_fill_manual(values = 
                      c(`CC BY` = "#B52141",
                        `CC BY-NC-ND` = "#0093c7",
                        `Els-User` = "grey80")) +
  labs(x = "Publication Year", y = "OA Percentage") +
  theme_minimal_hgrid() +
  theme(legend.position = "top",
        legend.justification = "right") +
  guides(fill = guide_legend("Open Content License"))
p_1
```

@@

```{r}
p <- cowplot::plot_grid(
  p_2, p_1,
  labels = "AUTO", ncol = 1
)
ggsave(here::here("figure", "license_portfolio.png"), p, dpi = 300, width = 6.5, height = 6)
```

>>>>

```{r}
library(cowplot)
p_1 <- year_per_oa_type_and_license %>%
  mutate(type_plot = case_when(
    type == "full_oa" ~ "Full OA",
    type == "hybrid_immediate_articles" ~ "Hybrid OA",
    type == "hybrid_delayed_articles" ~ "Delayed OA"
  )) %>% 
  mutate(type_plot = factor(type_plot, levels = c("Hybrid OA", "Full OA", "Delayed OA"))) %>%
  ggplot(aes(gsub("20", "'", as.character(issued_year)), prop, fill = license_code, group = license_code)) +
  geom_area(stat = "identity",
            color = "white",
            alpha = 0.8,
            position = position_stack(reverse = T)) +
  facet_grid(~type_plot) +
  scale_y_continuous(
  expand = expansion(mult = c(0, 0.0005)),
   labels = scales::percent_format(accuracy = 1),
   limits=c(0,.1),
   breaks = c(0, 0.03, 0.06, 0.09)) +
  scale_fill_manual(values = 
                      c(`CC BY` = "#B52141",
                        `CC BY-NC-ND` = "#0093c7",
                        `Els-User` = "grey80")) +
  labs(x = "Publication Year", y = "OA Percentage") +
  theme_minimal_hgrid() +
  theme(legend.position = "top",
        legend.justification = "right") +
  guides(fill = guide_legend("Open Content License"))
p_1
```

@@

```{r}
p <- cowplot::plot_grid(
  p_2, p_1,
  labels = "AUTO", ncol = 1
)
ggsave(here::here("figure", "license_portfolio.png"), p, dpi = 600, width = 6.5, height = 6)
```
